|

### 2021-08-16 paper/dcpo_demsupport.Rmd
use dotwhisker::small_multiple() to display AJPS results

# Theme setup
theme_set(theme_minimal())
```

@@

```{r formatResult-AJPS}
result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

@@

```{r coefName-AJPS}
index_coefName <- c(
    `Democracy\n (t-1)` = "Democracy[t-1]",
    `Democracy\n (t-2)` = "Democracy[t-2]",
    `Support\n (t-1)` = "Support[t-1]",
    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
)
```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}

type_model <-
  c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")

df_plot <- bind_rows(result_ajpsPooled, result_ajpsRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)))

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
      legend.title = element_blank()
    ) +
    scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

>>>>

# dotwhisker::small_multiple() hacks
body(small_multiple)[[17]] <- substitute(
  p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
                      x = as.factor(model), colour = submodel)) +
    do.call(geom_pointrange, point_args) + 
    ylab("") + xlab("") + 
    facet_grid(term ~ .,
               scales = "free",
               labeller = label_parsed,    # enable LaTeX facet labels
               switch = "y") +             # put facet labels on left
    scale_y_continuous(position = "right") # put axis label on right
)
```

@@

```{r formatResult-AJPS}
result_pooled <- bind_rows(
    mutate(result_clsAJPS[["pooled"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Pooled~OLS",
           model = "Model 1 (Pooled OLS)")

result_gmm <- bind_rows(
    mutate(result_clsAJPS[["gmm"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "System~GMM",
           model = "Model 3 (System GMM)")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = rep(
            c("Democracy\n (t-1)",
              "Democracy\n (t-2)",
              "Support\n (t-1)",
              "Log GDP\n per capita\n (t-1)",
              "GDP per\n capita growth\n (t-1)",
              "Regional\n democracy\n (t-1)",
              "Percent\n Muslim\n (t-1)",
              "Resource\n dependence\n (t-1)"),
            time = 6), 
        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
        submodel = factor(submodel, levels = c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2)))
    )

result_regime <- bind_rows(
    mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), submodel = "Uncertainty & More Data")
) %>% 
    mutate(type = "Pooled~OLS",
           model = "Model 2 (Pooled OLS)")

result_regimeGmm <- bind_rows(
    mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], submodel = "Point Estimates Only"),
    mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), submodel = "With Uncertainty"),
    mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), submodel = "Uncertainty & More Data")
)%>% 
    mutate(type = "System~GMM",
           model = "Model 4 (System GMM)")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
    filter(term != "(Intercept)") %>%
    mutate(
        term0 = rep(
            c("Democracy\n (t-1)",
              "Democracy\n (t-2)",
              "Support\n demo only\n (t-1)",
              "Support\n auto only\n (t-1)",
              "Log GDP\n per capita\n (t-1)",
              "GDP per\n capita growth\n (t-1)",
              "Regional\n democracy\n (t-1)",
              "Percent\n Muslim\n (t-1)",
              "Resource\n dependence\n (t-1)"),
            time = 6), 
        type = factor(type, levels = c("Pooled~OLS", "System~GMM")),
        submodel = factor(submodel, levels = c("Point Estimates Only","With Uncertainty", "Uncertainty & More Data")),
        model = factor(model, levels = paste0("Model ", rep(1:4), rep(c(" (Pooled OLS)", " (System GMM)"), each = 2))))

@@

# ```{r coefName-AJPS}
# index_coefName <- c(
#     `Democracy\n (t-1)` = "Democracy[t-1]",
#     `Democracy\n (t-2)` = "Democracy[t-2]",
#     `Support\n (t-1)` = "Support[t-1]",
#     `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
#     `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
#     `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
#     `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
#     `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
#     `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
#     `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
# )
# ```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=5, fig.height=10, fig.align='center'}

df_plot <- bind_rows(result_pooledAJPS, result_regimeAJPS) %>% 
    mutate(term = case_when(term0 == 'Democracy\n (t-1)' ~ "Democracy[t-1]",
                            term0 == 'Democracy\n (t-2)' ~ "Democracy[t-2]",
                            term0 == 'Support\n (t-1)' ~ "Democratic~Support[t-1]",
                            term0 == 'Support\n demo only\n (t-1)' ~ "Democratic~Support[t-1]~(democracies)",
                            term0 == 'Support\n auto only\n (t-1)' ~ "Democratic~Support[t-1]~(autocracies)",
                            term0 == 'Log GDP\n per capita\n (t-1)' ~ "Log~GDP~per~capita[t-1]",
                            term0 == 'GDP per\n capita growth\n (t-1)' ~ "GDP~per~capita~growth[t-1]",
                            term0 == 'Regional\n democracy\n (t-1)' ~ "Regional~Democracy[t-1]",
                            term0 == 'Percent\n Muslim\n (t-1)' ~ "Percent~Muslim[t-1]",
                            term0 == 'Resource\n dependence\n (t-1)' ~ "Resource~Dependence[t-1]",
                            TRUE ~ str_replace(term0, " ", "~")), 
           term = factor(term, levels =  c(
               "Democracy[t-1]",
               "Democracy[t-2]",
               "Democratic~Support[t-1]",
               "Democratic~Support[t-1]~(democracies)",
               "Democratic~Support[t-1]~(autocracies)",
               "Log~GDP~per~capita[t-1]",
               "GDP~per~capita~growth[t-1]",
               "Regional~Democracy[t-1]",
               "Percent~Muslim[t-1]",
               "Resource~Dependence[t-1]")))

small_multiple(df_plot, dot_args = list(size = .9, fatten = 1)) +
    theme_bw() +
    geom_hline(yintercept = 0, colour = "grey50", linetype = 2) +
    scale_color_grey(start = 0.8, end = 0.4, 
                     name = "Replication",
                     breaks=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data"),
                     labels=c("Point Estimates Only", "With Uncertainty", "Uncertainty & More Data")) +
    theme(axis.text.x  = element_text(angle = 90, hjust = .5),
          strip.text.y.left = element_text(angle = 0),
          legend.position = c(-0.115, -.01),
          legend.justification = c(1, 1), 
          legend.title = element_text(size = 9, face = "bold"),
          legend.title.align = 0.5,
          legend.text = element_text(size = 9),
          legend.background = element_rect(color="gray90"),
          legend.spacing = unit(-3, "pt"),
          legend.key.size = unit(9, "mm"))
